|

### 2021-05-10 appendix/appendix.Rmd
small edits to appendix text

The third phase consisted of filling out tables for each of the remaining 47
articles to systematically evaluate their eligibility. Since authors use
different measures for government spending and the number of lower/upper house
members, we extracted all coefficients that provided this information. In this
phase, we also collected information on whether the paper had been published,
and if it explicitly discussed the _law of 1/n_. Upon choosing the variables,
we excluded two studies from the first sample, as they did not have the
dependent/independent variables we collected for our meta-analysis. We then
included the 3 papers we found in the second search, as both conformed to our
criteria, and compiled our final sample of `r length(unique(dat$authoryear))`
articles.

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

```{r, fig.width=8, fig.height=5, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

>>>>

The third phase consisted of filling out tables for each of the remaining 47
articles to systematically evaluate their eligibility. Since authors use
different measures for government spending and the number of lower/upper house
members, we extracted all coefficients that provided this information. In this
phase, we also collected information on whether the paper had been published,
and if it explicitly discussed the _law of 1/n_. Upon choosing the variables,
we excluded two studies from the first sample, as they did not have the
dependent/independent variables we collected for our meta-analysis. We then
included the 2 papers we found in the second search, as both conformed to our
criteria, and compiled our final sample of `r length(unique(dat$authoryear))`
articles.

@@

```{r, fig.width=4, fig.height=3, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

```{r, fig.width=8, fig.height=3, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```
